Tropical Andes Taxonomic Diversity of Plants and Frugivores

### 2023-08-04 code/L2/L2_2_TropicalAndes_taxdiv.Rmd
add filtering occ records by trait species lists

@@

# Convert data to spatial data
```{r}
plants.sf <- st_as_sf(TropicalAndes_plant_occ_forest, coords = c("decimalLongitude", "decimalLatitude"), crs = 4326)

frugivores.sf <- st_as_sf(TropicalAndes_frugivore_occ_forest, coords = c("decimalLongitude", "decimalLatitude"), crs = 4326)
```

@@

```{r}
Forest_sf <- st_as_sf(Forest_poly)
Forest_sf
plot(Forest_sf)
```

@@

# Write data to csv
```{r}
write.csv(plant_cellRichness0.75, file.path(output_path,"TropicalAndes_GBIF_plant_richness.csv"))
write.csv(frugivore_cellRichness0.75, file.path(output_path,"TropicalAndes_frugivore_richness.csv"))
```

>>>>

# Filter plant occ by plant trait species list
```{r}
plant_trait_species_list <- read.csv(file.path(data_path,"TropicalAndes_plant_traits_forest_species_list.csv"))
TropicalAndes_plant_occ_forest_sub <- TropicalAndes_plant_occ_forest %>% filter(species %in% plant_trait_species_list$x)
write.csv(TropicalAndes_plant_occ_forest_sub, file.path(data_path,"TropicalAndes_plant_occ_forest_sub.csv"))
```

# Filter frugivore occ by frugivore trait species list
```{r}
frugivore_trait_species_list <- read.csv(file.path(data_path,"TropicalAndes_frugivore_traits_forest_species_list.csv"))
TropicalAndes_frugivore_occ_forest_sub <- TropicalAndes_frugivore_occ_forest %>% filter(species %in% frugivore_trait_species_list$x)
write.csv(TropicalAndes_frugivore_occ_forest_sub, file.path(data_path,"TropicalAndes_frugivore_occ_forest_sub.csv"))
```

@@

# Convert data to spatial data
```{r}
plants.sf <- st_as_sf(TropicalAndes_plant_occ_forest_sub, coords = c("decimalLongitude", "decimalLatitude"), crs = 4326)

frugivores.sf <- st_as_sf(TropicalAndes_frugivore_occ_forest_sub, coords = c("decimalLongitude", "decimalLatitude"), crs = 4326)
```

@@

```{r}
Forest_sf <- st_as_sf(Forest_poly)
Forest_sf
plot(Forest_sf)
st_write(Forest_sf, file.path(data_path, "Forest_sf.shp"))
```

@@

# Write data to csv
```{r}
write.csv(plant_cellRichness0.75, file.path(output_path,"TropicalAndes_GBIF_plant_richness_sub.csv"))
write.csv(frugivore_cellRichness0.75, file.path(output_path,"TropicalAndes_frugivore_richness.csv"))
```
